`r params$doc_title`

### 2023-04-04 scripts/MSc.Rmd
small dir changes

```{r MendelianRandomization-analysis, warning=FALSE}
## load results
est <- readRDS(file = dplyr::last(list.files("../output/Rdata/", pattern = "_est.rds", full.names = TRUE)))

>>>>

```{r MendelianRandomization-analysis, warning=FALSE}
## load results
est <- readRDS(file = dplyr::last(list.files("../output/Rdata/mr-results/", pattern = "_est.rds", full.names = TRUE)))
